Covariate analysis of ROSMAP reprocessed counts (with TMM normalisation)

### 2017-03-07 code/Rmd/ROSMAP_RNASeq_Reprocessed_TMM.Rmd
Minor modifications in ROSMAP reprocessed RNASeq to include picard metrics

## Requires ggdendro
devtools::source_url("https://raw.githubusercontent.com/chr1swallace/random-functions/master/R/ggplot-heatmap.R")

@@

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='AMPAD')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
# Download expression data
COUNT_ID <- 'syn7750270';
ALL_USED_IDs <- COUNT_ID
COUNT_OBJ <- synGet(COUNT_ID)
COUNT <- read.table(COUNT_OBJ@filePath,header=T,sep='\t',check.names = F)

@@

@@

# Match technical and clinical covariates
METADATA <- METADATA.TECH %>% 
  dplyr::select(-projid) %>%
  dplyr::left_join(KEY) %>%
  dplyr::left_join(METADATA.CLINICAL)

@@

### Covariate clustering
Determine relationship between covariates. 
```{r covariates.clustering, cache=TRUE}
#"braaksc","ceradsc","cts_mmse30_first_ad_dx","cts_mmse30_lv"
FactorCovariates <- c("Batch", "msex", "race", "spanish", "cogdx")
ContCovariates <- c("RINcontinuous","age_first_ad_dx","age_death","age_at_visit_max","pmi","educ")

@@

# Add in RIN^2 values
COVARIATES$RINcontinuous2 = COVARIATES$RINcontinuous^2
ContCovariates = c(ContCovariates, 'RINcontinuous2')
```
Correlation/association between covariates at an FDR <= 0.1
```{r covariates.correlation, fig.width=10, fig.height=10}
COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 0.05)
ggheatmap.show(COVARIATES.CORRELATION$plot, col.width=0.5, row.width=0.1)
```

```{r dataExplore, fig.width = 10, fig.height = 10}
# RIN
p = list()
p[[1]] = ggplot(COVARIATES, aes(x = cogdx, y = RINcontinuous)) + geom_boxplot()
p[[1]] = p[[1]] + ggtitle('RIN') + theme(legend.position = 'top')

@@

@@

Significant covariates to adjust at FDR 0.1 are `r preAdjustedSigCovars$significantCovars`
```{r preAdjustedSigCovars.NULL, fig.width=20, fig.height=12}
preAdjustedSigCovars[["PC_res"]][[2]]$plotData
```
### Normalisation (iterative design)
Since many covariates are correlated, re-normalising COUNTS with an iterative design matrix. Here "cogdx" is chosen as the primary variable of interest (i.e., covariate selection is conditioned on cognitive scores)

Adding Batch and msex a priori to variable selection
```{r customNorm, results='asis'}
# Primary variable of interest
postAdjustCovars = c('cogdx', 'Batch', 'msex');

# Assign residual covariates
residualSigCovars = preAdjustedSigCovars
covariatesEffects = residualSigCovars$Effects.significantCovars[setdiff(residualSigCovars$significantCovars, postAdjustCovars)]
postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects))) %>% unique()

@@

  # Residual covariates to choose from
  residCovars <- setdiff(c(FactorCovariates,ContCovariates), c(postAdjustCovars))

@@

  # Add postadjusted covariates (if any)
  covariatesEffects = residualSigCovars$Effects.significantCovars[setdiff(residualSigCovars$significantCovars, 
                                                                          c(postAdjustCovars))]

@@

### Sanity check
```{r residualSigCovars.manual, fig.width=12, fig.height=8}
residualSigCovars[["PC_res"]][[2]]$plotData
```

### Residual calculation
Calculate weighted residuals and add back "cogdx" to the residuals
```{r varsToAddBack}
# Add variable of interest back to the residuals
varsToAddIn = grep("cogdx", colnames(DM1$design), value = T)
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION + 
  VOOM.ADJUSTED.FIT$coefficients[,varsToAddIn] %*% t(DM1$design[,varsToAddIn])
```
Coexpression of genes 
```{r coexp2, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(RESIDUAL.GENE_EXPRESSION))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```

@@

# Query biomart
Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol"),
                       filters = "ensembl_gene_id", 
                       values = backgroundGenes$ensembl_gene_id,
                       mart = mart)

# Add gene names
RESIDUAL.GENE_EXPRESSION <- RESIDUAL.GENE_EXPRESSION %>%
  rownameToFirstColumn('gene.id') %>%
  left_join(backgroundGenes) %>%
  left_join(Ensemble2HGNC) %>%
  dplyr::select(gene.id, ensembl_gene_id, hgnc_symbol, one_of(rownames(COVARIATES)))

VOOM.ADJUSTED.GENE_EXPRESSION$E <- VOOM.ADJUSTED.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('gene.id') %>%
  left_join(backgroundGenes) %>%
  left_join(Ensemble2HGNC) %>%
  dplyr::select(gene.id, ensembl_gene_id, hgnc_symbol, one_of(rownames(COVARIATES)))
```

@@

### Differential expression analysis
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp, fig.height=6, fig.width=18}
# Fit contrast
contrast = makeContrasts(contrasts=c("cogdx1-cogdx2",
                                     "cogdx1-cogdx4",
                                     "cogdx2-cogdx4"),
                         levels = colnames(VOOM.ADJUSTED.FIT$coefficients))
FIT.CONTR = contrasts.fit(VOOM.ADJUSTED.FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)

# Get differnetial expression
DE = lapply(1:3, function(i, FIT, VOOM.ADJUSTED.GENE_EXPRESSION, Ensemble2HGNC){
  topTable(FIT.CONTR, coef=i, number = dim(VOOM.ADJUSTED.GENE_EXPRESSION$E)[1], confint = T) %>%
    rownameToFirstColumn('gene.id') %>%
    left_join(backgroundGenes) %>%
    left_join(Ensemble2HGNC) %>%
    dplyr::select(gene.id, ensembl_gene_id, hgnc_symbol, logFC, CI.L, CI.R, AveExpr, t, P.Value, adj.P.Val, B)
}, FIT, VOOM.ADJUSTED.GENE_EXPRESSION, Ensemble2HGNC) 
names(DE) = colnames(contrast)

DE = DE %>% 
  rbindlist(idcol = 'Comparison') %>%
  dplyr::mutate(Study = 'ROSMAP', Region = 'DLPFC',
                Direction = logFC/abs(logFC),
                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')))

@@

p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC)) + geom_point() + xlim(c(-1,1))
p = p + geom_hline(yintercept = -log10(0.05), color = 'red') 
p = p + geom_vline(xintercept = log2(1.2), color = 'red') 
p = p + geom_vline(xintercept = -log2(1.2), color = 'red') 
p = p + facet_grid(.~Comparison, scales = 'fixed')
p
```

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "ROSMAP Reprocessed RNASeq TMM (Based on cogdx)", parentId = parentId)
annotations(CODE) = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'Reprocessed RNAseq',

@@

# Store covariates
COVARIATES = rownameToFirstColumn(COVARIATES, 'Sampleid')
write.table(COVARIATES, file = 'ROSMAP_DLPFC_Covariates.tsv', sep = '\t', row.names=F, quote=F)
COV_OBJ = File('ROSMAP_DLPFC_Covariates.tsv', name = 'Covariates', parentId = CODE$properties$id)
COV_OBJ = synStore(COV_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)

# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix %>%
  as.matrix() %>% rownameToFirstColumn('gene.id') %>%
  write.table(file = 'ROSMAP_DLPFC_Counts.tsv', sep = '\t', row.names=F, quote=F)
COUNT_OBJ = File('ROSMAP_DLPFC_Counts.tsv', name = 'Raw counts (filtered)', parentId = CODE$properties$id)
COUNT_OBJ = synStore(COUNT_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                     executed = thisFile, activityDescription = activityDescription)

# Store logCPM
write.table(VOOM.ADJUSTED.GENE_EXPRESSION$E, file = 'ROSMAP_DLPFC_logCPM.tsv', sep = '\t', row.names=F, quote=F)
LCOUNT_OBJ = File('ROSMAP_DLPFC_logCPM.tsv', name = 'Raw counts (logCPM)', parentId = CODE$properties$id)
LCOUNT_OBJ = synStore(LCOUNT_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)

# Store design matrix
write.table(DM1$design, file = 'ROSMAP_DLPFC_Design.tsv', sep = '\t', row.names=F, quote=F)
DM_OBJ = File('ROSMAP_DLPFC_Design.tsv', name = 'Design Matrix', parentId = CODE$properties$id)
DM_OBJ = synStore(DM_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                  executed = thisFile, activityDescription = activityDescription)

# Store residual gene expression
write.table(RESIDUAL.GENE_EXPRESSION, file = 'ROSMAP_DLPFC_Expression.tsv', sep = '\t', row.names=F, quote=F)
EXP_OBJ = File('ROSMAP_DLPFC_Expression.tsv', name = 'Normalised Adjusted Residual Expression (Dx added)', parentId = CODE$properties$id)
EXP_OBJ = synStore(EXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)

# Store differential expression results
write.table(DE, file = 'ROSMAP_DLPFC_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('ROSMAP_DLPFC_DiffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
DEXP_OBJ = synStore(DEXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)
```
|  *Results*                |  *SynapseID*                     |
|  -------                  |   ---------                      |
|  Covariates               |  `r COV_OBJ$properties$id`       |
|  Raw counts (log CPM)     |  `r COUNT_OBJ$properties$id`     |
|  Design Matrix            |  `r DM_OBJ$properties$id`        |
|  Residual Expression      |  `r EXP_OBJ$properties$id`       |
|  Differential Expression  |  `r DEXP_OBJ$properties$id`      |

>>>>

@@

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='AMPAD')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
# Download expression data
COUNT_ID <- 'syn7750270';
ALL_USED_IDs <- COUNT_ID
COUNT_OBJ <- synGet(COUNT_ID)
COUNT <- read.table(COUNT_OBJ@filePath,header=T,sep='\t',check.names = F)
COUNT[,grep('150_120419', colnames(COUNT))[2]] = NULL

@@

# Get picard metrics from synapse
METADATA.PICARD_ID <- 'syn8380366'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.PICARD_ID
METADATA.PICARD_FPATHS <- untar(synGet(METADATA.PICARD_ID)@filePath, list = TRUE)
METADATA.PICARD_FPATHS = METADATA.PICARD_FPATHS[grep('picard.CombinedMetrics.csv', METADATA.PICARD_FPATHS)]
METADATA.PICARD <- plyr::ldply(METADATA.PICARD_FPATHS, read.csv)

METADATA.PICARD$Sampleid = gsub('picard/', '', METADATA.PICARD_FPATHS) %>%
  gsub('Aligned.out/picard.CombinedMetrics.csv','',.)
colnames(METADATA.PICARD) = gsub('AlignmentSummaryMetrics__','',colnames(METADATA.PICARD))
colnames(METADATA.PICARD) = gsub('RnaSeqMetrics__','',colnames(METADATA.PICARD))

@@

# Match technical and clinical covariates
METADATA <- METADATA.TECH %>%
  left_join(METADATA.PICARD) %>%
  dplyr::select(-projid) %>%
  dplyr::left_join(KEY) %>%
  dplyr::left_join(METADATA.CLINICAL)

@@

### Covariate clustering
Determine relationship between covariates
```{r covariates.clustering, cache=TRUE}
#"braaksc","ceradsc","cts_mmse30_first_ad_dx","cts_mmse30_lv", "PF_INDEL_RATE", "PF_MISMATCH_RATE"
FactorCovariates <- c("Batch", "msex", "race", "spanish", "cogdx")
ContCovariates <- c("RINcontinuous","age_first_ad_dx","age_death","age_at_visit_max","pmi","educ", 
                    "PCT_PF_READS_ALIGNED", "PCT_CORRECT_STRAND_READS", "PCT_INTERGENIC_BASES", 
                    "PCT_INTRONIC_BASES", "PCT_RIBOSOMAL_BASES", "PCT_USABLE_BASES")

@@

# Add in RIN^2 values
COVARIATES$RINcontinuous2 = COVARIATES$RINcontinuous^2
ContCovariates = c(ContCovariates, 'RINcontinuous2')
```
Correlation/association between covariates at an FDR <= 0.1
```{r covariates.correlation, fig.width=10, fig.height=10}
COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 0.05)
draw(COVARIATES.CORRELATION$plot, heatmap_legend_side = 'left')
```

```{r dataExplore, fig.width = 10, fig.height = 14}
# RIN
p = list()
p[[1]] = ggplot(COVARIATES, aes(x = cogdx, y = RINcontinuous)) + geom_boxplot()
p[[1]] = p[[1]] + ggtitle('RIN') + theme(legend.position = 'top')

@@

# Intronic bases
p[[5]] = ggplot(COVARIATES, aes(x = cogdx, y = PCT_INTRONIC_BASES)) + geom_boxplot()
p[[5]] = p[[5]] + ggtitle('Fraction Intronic Bases') + theme(legend.position = 'top')

# Ribosomal bases
p[[6]] = ggplot(COVARIATES, aes(x = cogdx, y = PCT_RIBOSOMAL_BASES)) + geom_boxplot()
p[[6]] = p[[6]] + ggtitle('Fraction Ribosomal Bases') + theme(legend.position = 'top')

@@

Significant covariates to adjust at FDR 0.1 are `r preAdjustedSigCovars$significantCovars`
```{r preAdjustedSigCovars.NULL, fig.width=20, fig.height=12}
preAdjustedSigCovars[["PC_res"]][[2]]$plotData
```
### Normalisation (iterative design)
Since many covariates are correlated, re-normalising COUNTS with an iterative design matrix. Adding Batch and msex a priori to variable selection
```{r customNorm, results='asis'}
# Primary variable of interest
postAdjustCovars = c('Batch', 'msex');

# Assign residual covariates
residualSigCovars = preAdjustedSigCovars
covariatesEffects = residualSigCovars$Effects.significantCovars[setdiff(residualSigCovars$significantCovars,
                                                                        c(postAdjustCovars, 'cogdx'))]
postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects))) %>% unique()

@@

  # Residual covariates to choose from
  residCovars <- setdiff(c(FactorCovariates,ContCovariates), c(postAdjustCovars, 'cogdx'))

@@

  # Add postadjusted covariates (if any)
  covariatesEffects = residualSigCovars$Effects.significantCovars[setdiff(residualSigCovars$significantCovars, 
                                                                          c(postAdjustCovars, 'cogdx'))]

@@

### Sanity check
```{r residualSigCovars.manual, fig.width=12, fig.height=8}
# Find PC of residual gene expression and significant covariates that are highly correlated with PCs
residualSigCovars = runPCAandPlotCorrelations(RESIDUAL.GENE_EXPRESSION, 
                                              COVARIATES,
                                              'adjusted design(voom-normalized)',
                                              isKeyPlot=TRUE)

residualSigCovars[["PC_res"]][[2]]$plotData
```
Coexpression of genes 
```{r coexp2, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(RESIDUAL.GENE_EXPRESSION))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```

@@

# Query biomart
Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol"),
                       filters = "ensembl_gene_id", 
                       values = backgroundGenes$ensembl_gene_id,
                       mart = mart)
```

@@

### Differential expression analysis
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp, fig.height=6, fig.width=18}
# Get design matrix
DESIGN = getDesignMatrix(COVARIATES[, 'cogdx', drop = F], Intercept = F)
DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]

# Fit linear model with residual expression
FIT = lmFit(RESIDUAL.GENE_EXPRESSION, design = DESIGN$design)

# Fit contrast
contrast = makeContrasts(contrasts=c("cogdx1-cogdx2",
                                     "cogdx1-cogdx4",
                                     "cogdx2-cogdx4"),
                         levels = colnames(FIT$coefficients))
FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)

# Get differnetial expression
DE = lapply(1:3, function(i, FIT, RESID.EXPR, backgroundGenes, Ensemble2HGNC){
  topTable(FIT.CONTR, coef=i, number = dim(RESID.EXPR)[1], confint = T) %>%
    rownameToFirstColumn('gene.id') %>%
    left_join(backgroundGenes) %>%
    left_join(Ensemble2HGNC) %>%
    dplyr::select(gene.id, ensembl_gene_id, hgnc_symbol, logFC, CI.L, CI.R, AveExpr, t, P.Value, adj.P.Val, B)
}, FIT, RESIDUAL.GENE_EXPRESSION, backgroundGenes, Ensemble2HGNC) 
names(DE) = colnames(contrast)

DE = DE %>% 
  rbindlist(idcol = 'Comparison') %>%
  dplyr::mutate(Study = 'ROSMAP', Region = 'DLPFC',
                Direction = logFC/abs(logFC),
                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
                Direction = as.character(Direction))
DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'

@@

p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
p = p + scale_color_manual(values = c('green','grey','red'))
p = p + facet_grid(.~Comparison, scales = 'fixed')
p
```

### Associate differential expression results with gc content and gene length
```{r associate.de}
geneLength.GCcontent = EDASeq::getGeneLengthAndGCContent(unique(DE$ensembl_gene_id), 
                                                        org = 'hsa', 
                                                        mode = "biomart") %>%
  rownameToFirstColumn('ensembl_gene_id')

tmp = left_join(DE, geneLenth.GCcontent)

pl = list()
pl[[1]] = ggplot(tmp, aes(y = log10(length), x = abs(logFC))) + 
  geom_point() + 
  stat_smooth(method=glm, se = TRUE, na.rm = T)
pl[[2]] = ggplot(tmp, aes(y = gc, x = abs(logFC))) + 
  geom_point() + 
  stat_smooth(method=glm, se = TRUE, na.rm = T)
pl[[3]] = ggplot(tmp, aes(y = log10(length), x = adj.P.Val)) + 
  geom_point() + 
  stat_smooth(method=glm, se = TRUE, na.rm = T)
pl[[4]] = ggplot(tmp, aes(y = gc, x = adj.P.Val)) + 
  geom_point() + 
  stat_smooth(method=glm, se = TRUE, na.rm = T)

multiplot(plotlist = pl, cols = 2)
```

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Add gene names
RESIDUAL.GENE_EXPRESSION <- RESIDUAL.GENE_EXPRESSION %>%
  rownameToFirstColumn('gene.id') %>%
  left_join(backgroundGenes) %>%
  left_join(Ensemble2HGNC) %>%
  dplyr::select(gene.id, ensembl_gene_id, hgnc_symbol, one_of(rownames(COVARIATES)))

VOOM.ADJUSTED.GENE_EXPRESSION$E <- VOOM.ADJUSTED.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('gene.id') %>%
  left_join(backgroundGenes) %>%
  left_join(Ensemble2HGNC) %>%
  dplyr::select(gene.id, ensembl_gene_id, hgnc_symbol, one_of(rownames(COVARIATES)))

# Code
CODE <- Folder(name = "ROSMAP Reprocessed RNASeq TMM (Based on cogdx)", parentId = parentId)
annotations(CODE) = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'Reprocessed RNAseq',

@@

# Store covariates
COVARIATES = rownameToFirstColumn(COVARIATES, 'Sampleid')
write.table(COVARIATES, file = 'ROSMAP_DLPFC_Covariates.tsv', sep = '\t', row.names=F, quote=F)
COV_OBJ = File('ROSMAP_DLPFC_Covariates.tsv', name = 'Covariates', parentId = CODE$properties$id)
annotations(COV_OBJ) = annotations(CODE)
annotations(COV_OBJ)$dataSubType = 'covariates'
COV_OBJ = synStore(COV_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)

# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix %>%
  as.matrix() %>% rownameToFirstColumn('gene.id') %>%
  write.table(file = 'ROSMAP_DLPFC_Counts.tsv', sep = '\t', row.names=F, quote=F)
COUNT_OBJ = File('ROSMAP_DLPFC_Counts.tsv', name = 'Raw counts (filtered)', parentId = CODE$properties$id)
annotations(COUNT_OBJ) = annotations(CODE)
annotations(COUNT_OBJ)$dataSubType = 'filteredCounts'
COUNT_OBJ = synStore(COUNT_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                     executed = thisFile, activityDescription = activityDescription)

# Store logCPM
write.table(VOOM.ADJUSTED.GENE_EXPRESSION$E, file = 'ROSMAP_DLPFC_logCPM.tsv', sep = '\t', row.names=F, quote=F)
LCOUNT_OBJ = File('ROSMAP_DLPFC_logCPM.tsv', name = 'Raw counts (logCPM)', parentId = CODE$properties$id)
annotations(LCOUNT_OBJ) = annotations(CODE)
annotations(LCOUNT_OBJ)$dataSubType = 'logcpm'
LCOUNT_OBJ = synStore(LCOUNT_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)

# Store design matrix
write.table(DM1$design, file = 'ROSMAP_DLPFC_Design.tsv', sep = '\t', row.names=F, quote=F)
DM_OBJ = File('ROSMAP_DLPFC_Design.tsv', name = 'Design Matrix', parentId = CODE$properties$id)
annotations(DM_OBJ) = annotations(CODE)
annotations(DM_OBJ)$dataSubType = 'designMatrix'
DM_OBJ = synStore(DM_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                  executed = thisFile, activityDescription = activityDescription)

# Store residual gene expression
write.table(RESIDUAL.GENE_EXPRESSION, file = 'ROSMAP_DLPFC_Expression.tsv', sep = '\t', row.names=F, quote=F)
EXP_OBJ = File('ROSMAP_DLPFC_Expression.tsv', name = 'Normalised Adjusted Residual Expression (Dx added)', 
               parentId = CODE$properties$id)
annotations(EXP_OBJ) = annotations(CODE)
annotations(EXP_OBJ)$dataSubType = 'residualGeneExp'
EXP_OBJ = synStore(EXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)

# Store differential expression results
write.table(DE, file = 'ROSMAP_DLPFC_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('ROSMAP_DLPFC_DiffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
annotations(DEXP_OBJ) = annotations(CODE)
annotations(DEXP_OBJ)$dataSubType = 'diffExp'
DEXP_OBJ = synStore(DEXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)
```
|  *Results*                |  *SynapseID*                     |
|  -------                  |   ---------                      |
|  Covariates               |  `r COV_OBJ$properties$id`       |
|  Raw counts (log CPM)     |  `r COUNT_OBJ$properties$id`     |
|  Design Matrix            |  `r DM_OBJ$properties$id`        |
|  Residual Expression      |  `r EXP_OBJ$properties$id`       |
|  Differential Expression  |  `r DEXP_OBJ$properties$id`      |
